Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-11 paper/structureScene.tex
write transition IV -> V

@@

Wavelets
$\boldsymbol{\psi_{\gamma_1}}(t)$ and $\boldsymbol{\psi_{\gamma_2}}(t)$ are designed as fourth-order Gammatone
wavelets with one vanishing moment \cite{Venkitaraman2014} \ml{missing ref}, as shown in Figure \ref{fig:gammatones}.
In the context of auditory scene analysis, the asymmetric envelope of Gammatone wavelets is more biologically plausible than the symmetric, Gaussian-like envelope of the widespread Morlet wavelets.
Indeed, it allows to reproduce two important psychoacoustic effects in the mammalian cochlea: the asymmetry of temporal masking and the asymmetry of spectral masking \cite{Fastl2007}.
Moreover, it should be noted that Gammatone wavelets follow the typical amplitude profile of natural sounds, beginning with a relatively sharp attack and ending with a slower decay. \ml{tu peux citer le travail publié a Nature de lewicki, qui montrent que ces formes se retrouvent par ICA de sons naturels http://www.cs.cmu.edu/~learning/talks-2002/02-10-21.lewicki.pdf}

>>>>

\vl{missing transition}

@@

Wavelets
$\boldsymbol{\psi_{\gamma_1}}(t)$ and $\boldsymbol{\psi_{\gamma_2}}(t)$ are designed as fourth-order Gammatone
wavelets with one vanishing moment \cite{Venkitaraman2014} \ml{missing ref}, as shown in Figure \ref{fig:gammatones}.
In the context of auditory scene analysis, the asymmetric envelope of Gammatone wavelets is more biologically plausible than the symmetric, Gaussian-like envelope of the widespread Morlet wavelets.
Indeed, it allows to reproduce two important psychoacoustic effects in the mammalian cochlea: the asymmetry of temporal masking and the asymmetry of spectral masking \cite{Fastl2007}.
Moreover, it should be noted that Gammatone wavelets follow the typical amplitude profile of natural sounds, beginning with a relatively sharp attack and ending with a slower decay.
As such, they can be discovered by unsupervised encoding of natural sounds \cite{Smith2006}.

The next section introduces some techniques in feature design to improve auditory scene classification with scattering coefficients.
